---
title: "Camino Itinerary"
author: "Mark Reuter"
date: '2024-02-13'
output: html_document
---

<!-- https://www.caminosantiagocompostela.com/camino-frances-route/ -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)

#### functions ####
mapFunction <- function(lat,long){
  simplemap <- leaflet()
  simplemap <- addTiles(simplemap)
  simplemap <- addMarkers(simplemap,
                          lng=long,
                          lat=lat,
                          #popup= "Starting Coord",
                          #label = "Starting Coord",
                          #icon = homeIcon,
                          labelOptions = labelOptions(noHide = TRUE))
  return(simplemap)
}

doubleMarkerMapFunction <- function(lat, long, lat2, long2){
  doublemap <- leaflet()
  doublemap <- addTiles(doublemap)
  doublemap <- addMarkers(doublemap,
                          lng=long,
                          lat=lat,
                          #popup= "Starting Coord",
                          label = "Start",
                          #icon = homeIcon,
                          labelOptions = labelOptions(noHide = TRUE))
  doublemap <- addMarkers(doublemap,
                          lng=long2,
                          lat=lat2,
                          #popup= "Starting Coord",
                          label = "End",
                          #icon = homeIcon,
                          labelOptions = labelOptions(noHide = TRUE))
  return(doublemap)
}

tripleMarkerMapFunction <- function(lat, long, lat2, long2, lat3, long3){
  triplemap <- leaflet()
  triplemap <- addTiles(triplemap)
  triplemap <- addMarkers(triplemap,
                          lng=long,
                          lat=lat,
                          #popup= "Starting Coord",
                          label = "Start",
                          #icon = homeIcon,
                          labelOptions = labelOptions(noHide = TRUE))
  triplemap <- addMarkers(triplemap,
                          lng=long2,
                          lat=lat2,
                          #popup= "Starting Coord",
                          label = "midway",
                          #icon = homeIcon,
                          labelOptions = labelOptions(noHide = TRUE))
  triplemap <- addMarkers(triplemap,
                          lng=long3,
                          lat=lat3,
                          #popup= "Starting Coord",
                          label = "End",
                          #icon = homeIcon,
                          labelOptions = labelOptions(noHide = TRUE))
  return(triplemap)
}

```

# Full Itinerary 715 km (approx 14 miles per day)
### Transit to Spain
#### London Stansted (13:50) to Zaragoza (17:05) (2024/04/26)
#### Zaragoza (11:06) to Pamplona (13:05) (2024/04/27)

### Leg 1 - 24 km

#### Day 1 - Pamplona to Puente la Reina - 24 km (2024/04/28)
### Leg 2 - 22 km
#### Day 2 - Puenta la Reina to Estella - 22 km (2024/04/29)
### Leg 3 - 50 km
#### Day 3 - Estella to Los Arcos 22 km (2024/04/30)
#### Day 4 - Los Arcos to Logrono 28 km (2024/05/01)
### Leg 4 - 125 km
#### Day 5 - Logrono to Nájera 30 km (2024/05/02)
#### Day 6 - Nájera to Santo Domingo de la Calzada 21 km (2024/05/03)
#### Day 7 - Santo Domingo de la Calzada to Belorado 23 km (2024/05/04)
#### Day 8 - Belorado to San Juan de Ortega 24 km (2024/05/05)
#### Day 9 - San Juan de Ortega to Buros 27 km (2024/05/06)
### Leg 5 - 184 km
#### Day 10 - Burgos to Hontanas 32 km (2024/05/07)
#### Day 11 - Hontanas to Boadilla del Camino 29 km (2024/05/08)
#### Day 12 - Boadilla del Camino to Carrión de los Condes 26 km (2024/05/09)
#### Day 13 - Carrión de los Condes to Terradillos de los Templarios 27 km (2024/05/10)
#### Day 14 - Terradillos de los Templarios to Bercianos del Real Camino 24 km (2024/05/11)
#### Day 15 - Bercianos del Real Camino to Mansilla de las Mulas 27 km (2024/05/12)
#### Day 16 - Mansilla de las Mulas to León 19 km (2024/05/13)
### Leg 6 - 50 km
#### Day 17 - Leon to Villadangos del Páramo 21 km (2024/05/14)
#### Day 18 - Villadangos del Páramo to Astorga 29 km (2024/05/15)
#### Day 19 - Rest day in Astorga (2024/05/16)
### Leg 7 - 167 km
#### Day 20 - Astorga to Rabanal del Camino 20 km (2024/05/17)
#### Day 21 - Rabanal del Camino to Molinaseca 25 km (2024/05/18)
#### Day 22 - Molinaseca to Villafranca del Bierzo 32 km (2024/05/19)
#### Day 23 - Villafranca del Bierzo to O Cebreiro 28 km (2024/05/20)
#### Day 24 - O Cebreiro to Triacastela 21 km (2024/05/21)
#### Day 25 - Triacastela to Sarria 19 km (2024/05/22)
#### Day 26 - Sarria to Portomarín 22 km (2024/05/23)
### Leg 8 - 93 km
#### Day 27 - Portomarín to Palas de Rei 25 km (2024/05/24)
#### Day 28 - Palas de Rei to Melide 15 km (2024/05/25)
#### Day 29 - Melide to Arzúa 14 km (2024/05/26)
#### Day 30 - Arzúa to Pedrouzo 19 km (2024/05/27)
#### Day 31 - Pedrouzo to Santiago de Compostela 20 km (2024/05/28)
#### Day 32 - Rest day or transit (2024/05/29)


### Flight from Santiago to xxx 2024/05/30

## Zaragosa

### Hotel Paris Centro, C. de San Pablo, 19, Casco Antiguo, 50003 Zaragoza, Spain
[Hotel Paris Centro](https://maps.app.goo.gl/NcyLKZd5FhevnLvJA)

```{r zaragosa, echo=FALSE}
hotelpariscentroLat <- 41.65558963141877
hotelpariscentroLong <- -0.8847546320320065
zara <- mapFunction(hotelpariscentroLat,
                    hotelpariscentroLong)
zara

```


# Leg 1 Pamplona to Puente la Reina - 24 km

### Pamplona to Puente la Reina 24 km (15 m), rolling hills

## Pamplona
### Albergue Jesus y Maria C. de la Compañía, 4, 31001 Pamplona, Navarra, Spain
[Albergue Jesus y Maria](https://maps.app.goo.gl/TpqQbmm41fEBi7ou5)

```{r coord, echo=FALSE}
PamplomaHostelLat <- 42.818951
PamplomaHostelLong <- -1.641751

PuentelaReinaLat <- 42.67220603137471
PuentelaReinaLong <- -1.8121066116168143

EstellaLat <- 42.67000344803912
EstellaLong <- -2.0274108652911202

LosArcosLat <- 42.569192091819644
LosArcosLong <- -2.194411176424429

LogronoLat <- 42.46831622437214
LogronoLong <- -2.444750263441197

BurgosLat <- 42.342478404175644
BurgosLong <- -3.703840141019459

LeonLat <- 42.59500116946184
LeonLong <- -5.568238657114206

AstorgaLat <- 42.45312258716735
AstorgaLong <- -6.051251641448496

PonferradaLat <- 42.54811231971199
PonferradaLong <- -6.597454689916324

SarriaLat <- 42.777517304932005
SarriaLong <- -7.413656717067121

SantiagoLat <- 42.88555802646954
SantiagoLong <- -8.523559289899342

SantiagoCathedralLat <- 42.88051766067628
SantiagoCathedralLong <- -8.544459062897769

najeraLat <- 42.41518571727236
najeraLong <- -2.7342653273102417

calzadaLat <- 42.44089270700817
calzadaLong <- -2.9525016235960213

beloradoLat <- 42.41958914931443
beloradoLong <- -3.188306627956277

sanjuandeortegaLat <- 42.37574310983867
sanjuandeortegaLong <- -3.4359024417225346

hontanasLat = 42.31271139905313
hontanasLong = -4.044831121209889

boadillaLat <- 42.25807861269066
boadillaLong <- -4.346444486186042

carrioncondesLat <- 42.33782498950543
carrioncondesLong <- -4.6016265069559905

templariosLat <- 42.36249858959254
templariosLong <- -4.8905992952307775

bercianosLat <- 42.3863995832578
bercianosLong <- -5.146526825508516

mulasLat <- 42.49721561257988
mulasLong <- -5.415637963474257

villadangosLat <- 42.51953279486428
villadangosLong <- -5.765354980533717

rabanalLat <- 42.48074479295968
rabanalLong <- -6.28419417870296

molinasecaLat <- 42.53736995266289
molinasecaLong <- -6.519802874515314

villafrancaLat <- 42.604573281713144
villafrancaLong <- -6.806612831494416

cebreiroLat <- 42.707755275994074
cebreiroLong <- -7.046090101818447

triacastelaLat <- 42.75529203442347
triacastelaLong <- -7.235265232211591

sarriaLat <- 42.77747684221717
sarriaLong <- -7.413576584786306

portomarinLat <- 42.80847380954628
portomarinLong <- -7.614967919461615

palasdeReiLat <- 42.87303757049406
palasdeReiLong <- -7.868961813909375

melideLat <- 42.91441691721295
melideLong <- -8.018225067785762

arzuaLat <- 42.92731979108971
arzuaLong <- -8.163986121672256

predrouzoLat <- 42.906884839466386
predrouzoLong <- -8.35914427187802

```

```{r pamploma, echo=FALSE}
pamploma <- mapFunction(PamplomaHostelLat,PamplomaHostelLong)
pamploma

```

## Puente la Reina

### Albergue Gares, Cortes de Navarra, 11, 31100 Puente la Reina, Navarra, Spain
[Albergue Gares](https://maps.app.goo.gl/7VxahNEQ7QnJA8Hr7)

```{r puentelareina, echo=FALSE}
puentelareina <- mapFunction(PuentelaReinaLat,PuentelaReinaLong)
puentelareina

```

# Leg 1

```{r leg1, echo=FALSE}
leg1 <- doubleMarkerMapFunction(PamplomaHostelLat,PamplomaHostelLong,PuentelaReinaLat,PuentelaReinaLong)
leg1

```

---

# Leg 2 Puenta la Reina to Estella - 22 km

### Puenta la Reina to Estella 22km (14 miles), rolling hills

## Estella

### Albergue de peregrinos de Estella La Rua, 50, 31200 Estella, Navarra, Spain
[Albergue de peregrinos de Estella](https://maps.app.goo.gl/YV4csc71bs5R53zA7)

```{r estella, echo=FALSE}
estella <- mapFunction(EstellaLat,EstellaLong)
estella

```

# Leg 2

```{r leg2, echo=FALSE}
leg2 <- doubleMarkerMapFunction(PuentelaReinaLat,PuentelaReinaLong,EstellaLat,EstellaLong)
leg2

```

---

## Leg 3 Estella to Logrono 50 km

### Estella to Los Arcos 22 km (14 miles) rolling hills

### Los Arcos to Logrono 28 km (17 miles) flat and rolling hills

## Los Arcos

### Public Albergue in Los Arcos, C. San Lázaro, 8, 31210 Los Arcos, Navarra, Spain
[Albergue de peregrinos Isaac Santiago, Los Arcos](https://www.alberguescaminosantiago.com/albergues/albergue-de-peregrinos-isaac-santiago-los-arcos-navarra/)

```{r losarcos, echo=FALSE}
losarcos <- mapFunction(LosArcosLat,LosArcosLong)
losarcos

```

## Logroño

### Albergue Municipal de Logroño C. Ruavieja, 32, 26001 Logroño, La Rioja, Spain
[Albergue Municipal de Logroño](https://maps.app.goo.gl/VcTVqBW3vrXhuBUu8)

```{r logrono, echo=FALSE}
logrono <- mapFunction(LogronoLat,LogronoLong)
logrono

```

# Leg 3

```{r leg3a, echo=FALSE}
leg3 <- tripleMarkerMapFunction(EstellaLat,
                                EstellaLong,
                                LosArcosLat,
                                LosArcosLong,
                                LogronoLat,
                                LogronoLong)
leg3

```

---

# Leg 4 Logrono to Burgos 125 km

### Logrono to Nájera 30 km (19 miles) mostly flat

### Nájera to Santo Domingo de la Calzada 21 km (13 miles) mostly flat

### Santo Domingo de la Calzada to Belorado 23 km (14 miles) mostly flat

### Belorado to San Juan de Ortega 24 km (15 miles) mostly flat

### San Juan de Ortega to Buros 27 km (17 miles) mostly flat

## Najera

### Albergue municipal peregrinos de Najera, 26300, Spain, La Rioja, Nájera
[Albergue municipal peregrinos de Najera](https://maps.app.goo.gl/xsajz2PkRjDiAP5T7)

```{r najera, echo=FALSE}
najera <- mapFunction(najeraLat,
                      najeraLong)
najera
```

## Santo Domingo de la Calzada

### Albergue Cofradía del Santo, C. Mayor, 42, Santo Domingo de la Calzada, La Rioja, Spain
[Albergue Cofradía del Santo](https://maps.app.goo.gl/XphZuaCcs5a6h8na9)

```{r calzada, echo=FALSE}
calzada <- mapFunction(calzadaLat,
                       calzadaLong)
calzada

```

## Belorado

### Albergue Belorado El Corro, C. Corro, 09250 Belorado, Burgos, Spain
[Albergue Belorado El Corro](https://maps.app.goo.gl/g6khEzKU3RtrihXV9)

```{r belorado, echo=FALSE}
belorado <- mapFunction(beloradoLat,
                        beloradoLong)
belorado

```

## San Juan de Ortega

### El Descanso de San Juan, 09199 San Juan de Ortega, Burgos, Spain
[El Descanso de San Juan](https://maps.app.goo.gl/ziX2CiJ9hXsupg6e7)

```{r sanjuandeortega, echo=FALSE}
sanjuandeortega <- mapFunction(sanjuandeortegaLat,
                               sanjuandeortegaLong)
sanjuandeortega

```

## Burgos

### Albergue de peregrinos Casa del Cubo de Burgos, C. de Fernán González, 28, 09003 Burgos, Spain
[Albergue de peregrinos Casa del Cubo de Burgos](https://maps.app.goo.gl/oXbdQF6WKKkK4CLJ6)


```{r burgos, echo=FALSE}
burgos <- mapFunction(BurgosLat,BurgosLong)
burgos

```


```{r leg4, echo=FALSE}
leg4 <- doubleMarkerMapFunction(LogronoLat,LogronoLong,BurgosLat,BurgosLong)
leg4

```

# Leg 4

```{r leg4completemap, echo=FALSE}
leg4complete <- leaflet(width=1000)
leg4complete <- addTiles(leg4complete)
leg4complete <- addMarkers(leg4complete,
                        lng=LogronoLong,
                        lat=LogronoLat,
                        #popup= "Starting Coord",
                        label = "Logrono",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))
leg4complete <- addMarkers(leg4complete,
                        lng=najeraLong,
                        lat=najeraLat,
                        #popup= "Starting Coord",
                        label = "Najera",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg4complete <- addMarkers(leg4complete,
                        lng=calzadaLong,
                        lat=calzadaLat,
                        #popup= "Starting Coord",
                        label = "Santo Domingo de la Calzada",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg4complete <- addMarkers(leg4complete,
                        lng=beloradoLong,
                        lat=beloradoLat,
                        #popup= "Starting Coord",
                        label = "Belorado",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg4complete <- addMarkers(leg4complete,
                        lng=sanjuandeortegaLong,
                        lat=sanjuandeortegaLat,
                        #popup= "Starting Coord",
                        label = "San Juan de Ortega",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg4complete <- addMarkers(leg4complete,
                        lng=BurgosLong,
                        lat=BurgosLat,
                        #popup= "Starting Coord",
                        label = "Burgos",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg4complete

```

---

# Leg 5 Burgos to Leon 184 km

### Burgos to Hontanas 32 km (20 miles) mostly flat
### Hontanas to Boadilla del Camino 29 km (18 miles) mostly flat
### Boadilla del Camino to Carrión de los Condes 26 km (16 miles) mostly flat
### Carrión de los Condes to Terradillos de los Templarios 27 km (17 miles) mostly flat
### Terradillos de los Templarios to Bercianos del Real Camino 24 km (15 miles) mostly flat
### Bercianos del Real Camino to Mansilla de las Mulas 27 km (17 miles) mostly flat
### Mansilla de las Mulas to León 19 km (12 miles) mostly flat

## Hontanas

### Albergue San Juan Municipal Hontanas, C. Real, 26, 09227 Hontanas, Burgos, Spain
[Albergue San Juan Municipal Hontanas](https://maps.app.goo.gl/wi2C4yUeKryHaUCZ8)

```{r hontanas, echo=FALSE}
hontanas <- mapFunction(hontanasLat,hontanasLong)
hontanas
```


## Boadilla del Camino

### Albergue En El Camino, C. Francos, 3, 34468 Boadilla del Camino, Palencia, Spain
[Albergue En El Camino](https://maps.app.goo.gl/CMttpVS2fnPipdHC6)

```{r boadilla, echo=FALSE}
boadilla <- mapFunction(boadillaLat,boadillaLong)
boadilla
```

## Carrión de los Condes

### Hostel Parish Santa Maria del Camino, C. Clérigo Pastor, 6, 34120 Carrión de los Condes, Palencia, Spain
[Hostel Parish Santa Maria del Camino](https://maps.app.goo.gl/2KqBj53C5r5Bdw2X8)

```{r carrioncondes, echo=FALSE}
carrioncondes <- mapFunction(carrioncondesLat,carrioncondesLong)
carrioncondes
```

## Terradillos de los Templarios

### Hostel Jacques De Molay, Calle Iglesia, 10, 34349 Terradillos de los Templarios, Palencia, Spain
[Hostel Jacques De Molay](https://maps.app.goo.gl/uPybQCtkNUkaJUh77)

```{r templarios, echo=FALSE}
templarios <- mapFunction(templariosLat,templariosLong)
templarios

```

## Bercianos del Real Camino

### Albergue Parroquial Casa Rectoral, C. la Iglesia, 41, 24325 Bercianos del Real Camino, León, Spain
[Albergue Parroquial Casa Rectoral](https://maps.app.goo.gl/EJyRyQEf3xChyqHq9)

```{r bercianos, echo=FALSE}
bercianos <- mapFunction(bercianosLat,bercianosLong)
bercianos
```

## Mansilla de las Mulas

### El Albergue de Gaia, Av. Constitución, 28, 24210 Mansilla de las Mulas, León, Spain
[El Albergue de Gaia](https://maps.app.goo.gl/u33ktpY6wuZGaBsF8)

```{r mulas, echo=FALSE}
mulas <- mapFunction(mulasLat,mulasLong)
mulas
```

## León
### Albergue at the Benedictine Sisters Convent, Pl. Sta. María del Camino, 7, 24003 León, Spain
[Albergue at the Benedictine Sisters Convent](https://maps.app.goo.gl/2BGyvtbgDWWb42Mz8)

```{r leon, echo=FALSE}
leon <- mapFunction(LeonLat,LeonLong)
leon
```

# Leg 5

```{r leg5complete, echo=FALSE}
leg5complete <- leaflet(width=1000)
leg5complete <- addTiles(leg5complete)
leg5complete <- addMarkers(leg5complete,
                        lng=BurgosLong,
                        lat=BurgosLat,
                        #popup= "Starting Coord",
                        label = "Burgos",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg5complete <- addMarkers(leg5complete,
                        lng=hontanasLong,
                        lat=hontanasLat,
                        #popup= "Starting Coord",
                        label = "Hontanas",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg5complete <- addMarkers(leg5complete,
                        lng=boadillaLong,
                        lat=boadillaLat,
                        #popup= "Starting Coord",
                        label = "Boadilla del Camino",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg5complete <- addMarkers(leg5complete,
                        lng=carrioncondesLong,
                        lat=carrioncondesLat,
                        #popup= "Starting Coord",
                        label = "Carrión de los Condes",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg5complete <- addMarkers(leg5complete,
                        lng=templariosLong,
                        lat=templariosLat,
                        #popup= "Starting Coord",
                        label = "Terradillos de los Templarios",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg5complete <- addMarkers(leg5complete,
                        lng=bercianosLong,
                        lat=bercianosLat,
                        #popup= "Starting Coord",
                        label = "Bercianos del Real Camino",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))


leg5complete <- addMarkers(leg5complete,
                        lng=mulasLong,
                        lat=mulasLat,
                        #popup= "Starting Coord",
                        label = "Mansilla de las Mulas",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg5complete <- addMarkers(leg5complete,
                        lng=LeonLong,
                        lat=LeonLat,
                        #popup= "Starting Coord",
                        label = "Leon",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg5complete
```

---

# Leg 6 Leon to Astorga - 50 km

### Leon to Villadangos del Páramo 21 km (13 miles) mostly flat
### Villadangos del Páramo to Astorga 29 km (18 miles) rolling hills

## Villadangos del Páramo

### Albergue de Peregrinos Municipal de "Villadangos del Páramo", Carr. de León - Astorga, 24392 Villadangos del Paramo, León, Spain
[Albergue de Peregrinos Municipal de "Villadangos del Páramo"](https://maps.app.goo.gl/nRt8j1Az4JGB94C6A)

```{r villadangos, echo=FALSE}
villadangos <- mapFunction(villadangosLat,
                           villadangosLong)
villadangos
```

## Astorga

### Albergue de peregrinos de Astorga, Plaza San Francisco, 3, 24700 Astorga, León, Spain
[Albergue de peregrinos de Astorga](https://maps.app.goo.gl/TK9eHkPDEWx63TZcA)


```{r astorga, echo=FALSE}
astorga <- mapFunction(AstorgaLat,AstorgaLong)
astorga
```

# Leg 6

```{r leg6, echo=FALSE}
leg6 <- tripleMarkerMapFunction(LeonLat,
                                LeonLong,
                                villadangosLat,
                                villadangosLong,
                                AstorgaLat,
                                AstorgaLong)
leg6

```

---

# Leg 7 Astorga to Portomarín - 167 km

### Astorga to Rabanal del Camino 20 km (12 miles) gradual climb
### Rabanal del Camino to Molinaseca 25 km (16 miles) mountains
### Molinaseca to Villafranca del Bierzo 32 km (20 miles) rolling hills
### Villafranca del Bierzo to O Cebreiro 28 km (17 miles) mountains
### O Cebreiro to Triacastela 21 km (13 miles) mountains
### Triacastela to Sarria 19 km (12 miles) rolling hills
### Sarria to Portomarín 22 km (14 miles) rolling hills

## Rabanal del Camino

### Albergue municipal de Rabanal del Camino, Pl. de Geronimo Moran Alonso, 24722 Rabanal del Camino, León, Spain
[Albergue municipal de Rabanal del Camino](https://maps.app.goo.gl/6hgbGmumBLQqF3yCA)

```{r rabanal, echo=FALSE}
rabanal <- mapFunction(rabanalLat,
                       rabanalLong)
rabanal
```

## Molinaseca

### Albergue Compostela, C. la Calleja, 3, 24413 Molinaseca, León, Spain
[Albergue Compostela](https://maps.app.goo.gl/ZgVLJUaZsCnpDqoR7)

```{r molinaseca, echo=FALSE}
molinaseca <- mapFunction(molinasecaLat,
                          molinasecaLong)
molinaseca
```

## Villafranca del Bierzo

### Public Albergue of Villafranca del Bierzo, 24500 Villafranca del Bierzo, León, Spain
[Public Albergue of Villafranca del Bierzo](https://maps.app.goo.gl/7uj54KDyjdFpk1Cm9)

```{r villafranca, echo=FALSE}
villafranca <- mapFunction(villafrancaLat,
                           villafrancaLong)
villafranca
```

## O Cebreiro

### Albergue Municipal de O Cebreiro, Lugar Cebreiro, 17, 27671 Pedrafita do Cebreiro, Lugo, Spain
[Albergue Municipal de O Cebreiro](https://maps.app.goo.gl/Sa5yqxxWUJFJmEsp6)

```{r cebreiro, echo=FALSE}
cebreiro <- mapFunction(cebreiroLat,
                        cebreiroLong)
cebreiro
```

## Triacastela

### Albergue Municipal de peregrinos de Triacastela, 27630 Triacastela, Lugo, Spain
[Albergue Municipal de peregrinos de Triacastela](https://maps.app.goo.gl/ygcvpcxvbVh9bEtJ8)

```{r triacastela, echo=FALSE}
triacastela <- mapFunction(triacastelaLat,
                           triacastelaLong)
triacastela
```

## Sarria

### Albergue municipal de peregrinos de Sarria, Rúa Maior, 79, 27600 Sarria, Lugo, Spain
[Albergue municipal de peregrinos de Sarria]()

```{r sarria, echo=FALSE}
sarria <- mapFunction(SarriaLat,SarriaLong)
sarria
```

## Portomarín

### Albergue de peregrinos de Portomarín, Rúa Fraga Iribarne, 7, 27170 Portomarín, Lugo, Spain
[Albergue de peregrinos de Portomarín](https://maps.app.goo.gl/2TkcRKcKkPye1tWE8)

```{r portomarin, echo=FALSE}
portomarin <- mapFunction(portomarinLat,
                          portomarinLong)
portomarin
```

<!-- ## Ponferrada -->

<!-- ### Albergue Alda Pilgrim Ponferrada, Av. de la Puebla, 46, 24400 Ponferrada, León, Spain -->
<!-- [Albergue Alda Pilgrim Ponferrada](https://maps.app.goo.gl/nurQEVhCrLZsidhj6) -->

<!-- ```{r ponferrada, echo=FALSE} -->
<!-- ponferrada <- mapFunction(PonferradaLat,PonferradaLong) -->
<!-- ponferrada -->
<!-- ``` -->

# Leg 7

```{r leg7, echo=FALSE}
leg7complete <- leaflet(width=1000)
leg7complete <- addTiles(leg7complete)

leg7complete <- addMarkers(leg7complete,
                        lng=AstorgaLong,
                        lat=AstorgaLat,
                        #popup= "Starting Coord",
                        label = "Astorga",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg7complete <- addMarkers(leg7complete,
                        lng=rabanalLong,
                        lat=rabanalLat,
                        #popup= "Starting Coord",
                        label = "Rabanal",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg7complete <- addMarkers(leg7complete,
                        lng=molinasecaLong,
                        lat=molinasecaLat,
                        #popup= "Starting Coord",
                        label = "Molinaseca",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg7complete <- addMarkers(leg7complete,
                        lng=villafrancaLong,
                        lat=villafrancaLat,
                        #popup= "Starting Coord",
                        label = "Villafranca del Bierzo",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg7complete <- addMarkers(leg7complete,
                        lng=cebreiroLong,
                        lat=cebreiroLat,
                        #popup= "Starting Coord",
                        label = "O Cebreiro",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg7complete <- addMarkers(leg7complete,
                        lng=triacastelaLong,
                        lat=triacastelaLat,
                        #popup= "Starting Coord",
                        label = "Triacastela",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg7complete <- addMarkers(leg7complete,
                        lng=sarriaLong,
                        lat=sarriaLat,
                        #popup= "Starting Coord",
                        label = "Sarria",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg7complete <- addMarkers(leg7complete,
                        lng=portomarinLong,
                        lat=portomarinLat,
                        #popup= "Starting Coord",
                        label = "Portomarín",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

leg7complete

```

---

# Leg 8 Portomarín to Santiago - 93 km

### Portomarín to Palas de Rei 25 km (16 miles) rolling hills
### Palas de Rei to Melide 15 km (9 miles) rolling hills
### Melide to Arzúa 14 km (9 miles) rolling hills
### Arzúa to Pedrouzo 19 km (12 miles) roling hills
### Pedrouzo to Santiago de Compostela 20 km (12 miles) rolling hills

## Palas de Rei

### Albergue de peregrinos de Palas de Rei, Av. Compostela, 19, 27200 Palas de Rei, Lugo, Spain
[Albergue de peregrinos de Palas de Rei](https://maps.app.goo.gl/KSRi8TuikQUsmNhh6)


```{r palasdeRei, echo=FALSE}
palasdeRei <- mapFunction(palasdeReiLat,
                          palasdeReiLong)
palasdeRei

```

## Melide

### Albergue Municipal de Peregrinos de Melide, Rúa San Antonio, 15800 Melide, A Coruña, Spain
[Albergue Municipal de Peregrinos de Melide](https://maps.app.goo.gl/nEaWwLsGDY3iNFUn9)


```{r melide, echo=FALSE}
melide <- mapFunction(melideLat,
                      melideLong)
melide

```

## Arzúa

### Albergue del Peregrino, Rúa de Ramón Franco, 7, 15810 Arzúa, A Coruña, Spain
[Albergue del Peregrino](https://maps.app.goo.gl/E1PHA5T8eQ8GMwzaA)


```{r arzua, echo=FALSE}
arzua <- mapFunction(arzuaLat,
                     arzuaLong)
arzua

```

## O Pedrouzo

### HOSTEL AZUL CIELO, Av. Lugo, 28, 15821 O Pedrouzo, A Coruña, Spain
[HOSTEL AZUL CIELO](https://maps.app.goo.gl/pdFs3RBcCoyUtHEE8)

```{r predrouzo, echo=FALSE}
predrouzo <- mapFunction(predrouzoLat,
                         predrouzoLong)
predrouzo

```

## Santiago

### ALBERGUE FIN DEL CAMINO, Rúa de Moscova, 15707 Santiago de Compostela, A Coruña, Spain
[Albergue Fin del Camino](https://maps.app.goo.gl/A4TUAgpbqAUpvhLN8)
[ALBERGUE FIN DEL CAMINO](https://alberguefindelcamino.com/?lang=en)

```{r santiagoAccomm, echo=FALSE}
santiago <- mapFunction(SantiagoLat,SantiagoLong)
santiago
```

# Leg 8

```{r leg8, echo=FALSE}
leg8complete <- leaflet(width=1000)
leg8complete <- addTiles(leg8complete)

leg8complete <- addMarkers(leg8complete,
                           lng=portomarinLong,
                           lat=portomarinLat,
                           #popup= "Starting Coord",
                           label = "Portomarín",
                           #icon = homeIcon,
                           labelOptions = labelOptions(noHide = TRUE)
                           )

leg8complete <- addMarkers(leg8complete,
                           lng=palasdeReiLong,
                           lat=palasdeReiLat,
                           #popup= "Starting Coord",
                           label = "Palas de Rei",
                           #icon = homeIcon,
                           labelOptions = labelOptions(noHide = TRUE)
                           )

leg8complete <- addMarkers(leg8complete,
                           lng=melideLong,
                           lat=melideLat,
                           #popup= "Starting Coord",
                           label = "Melide",
                           #icon = homeIcon,
                           labelOptions = labelOptions(noHide = TRUE)
                           )

leg8complete <- addMarkers(leg8complete,
                           lng=arzuaLong,
                           lat=arzuaLat,
                           #popup= "Starting Coord",
                           label = "Arzua",
                           #icon = homeIcon,
                           labelOptions = labelOptions(noHide = TRUE)
                           )

leg8complete <- addMarkers(leg8complete,
                           lng=predrouzoLong,
                           lat=predrouzoLat,
                           #popup= "Starting Coord",
                           label = "Predrouzo",
                           #icon = homeIcon,
                           labelOptions = labelOptions(noHide = TRUE)
                           )

leg8complete <- addMarkers(leg8complete,
                           lng=SantiagoLong,
                           lat=SantiagoLat,
                           #popup= "Starting Coord",
                           label = "Santiago",
                           #icon = homeIcon,
                           labelOptions = labelOptions(noHide = TRUE)
                           )

leg8complete
```


# Entire Route

```{r mastermap, echo=FALSE}
mastermap <- leaflet()
mastermap <- addTiles(mastermap)
mastermap <- addMarkers(mastermap,
                        lng=PamplomaHostelLong,
                        lat=PamplomaHostelLat,
                        #popup= "Starting Coord",
                        label = "Pamploma",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))
mastermap <- addMarkers(mastermap,
                        lng=PuentelaReinaLong,
                        lat=PuentelaReinaLat,
                        #popup= "Starting Coord",
                        label = "Puente la Reina",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))
mastermap <- addMarkers(mastermap,
                        lng=EstellaLong,
                        lat=EstellaLat,
                        #popup= "Starting Coord",
                        label = "Estella",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))
mastermap <- addMarkers(mastermap,
                        lng=LogronoLong,
                        lat=LogronoLat,
                        #popup= "Starting Coord",
                        label = "Logrono",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

mastermap <- addMarkers(mastermap,
                        lng=BurgosLong,
                        lat=BurgosLat,
                        #popup= "Starting Coord",
                        label = "Burgos",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

mastermap <- addMarkers(mastermap,
                        lng=LeonLong,
                        lat=LeonLat,
                        #popup= "Starting Coord",
                        label = "Leon",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

mastermap <- addMarkers(mastermap,
                        lng=AstorgaLong,
                        lat=AstorgaLat,
                        #popup= "Starting Coord",
                        label = "Astorga",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

mastermap <- addMarkers(mastermap,
                        lng=PonferradaLong,
                        lat=PonferradaLat,
                        #popup= "Starting Coord",
                        label = "Ponferrada",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

mastermap <- addMarkers(mastermap,
                        lng=SarriaLong,
                        lat=SarriaLat,
                        #popup= "Starting Coord",
                        label = "Sarria",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

mastermap <- addMarkers(mastermap,
                        lng=SantiagoCathedralLong,
                        lat=SantiagoCathedralLat,
                        #popup= "Starting Coord",
                        label = "Santiago",
                        #icon = homeIcon,
                        labelOptions = labelOptions(noHide = TRUE))

mastermap



```

